Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations.

### 2015-09-25 Outline.tex
Added bib file
Updates to annotations
Hand in of Outline for Peer Review

\usepackage[T1]{fontenc}  %% needed for special characters (umlaut)
\usepackage[latin1]{inputenc}
\usepackage{graphicx}     %% for graphical things such as including pictures
\usepackage{url}          %% for proper formatting of URLs

@@

\title{Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations. \thanks{wtf}}

% The abbreviated title will be shown in the headers of even pages.
% You should use the full title unless it is too long.
\titlerunning{Touch Interfaces for Robotic Nozzles}

@@

\subsection{Design of an A/B test}
In order to test if increased color contrast in a touch interface can completely remove all faulty interactions an A/B test was conducted.
\emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.

@@

\bibliography{demo}

>>>>

\usepackage[T1]{fontenc}  %% needed for special characters (umlaut)
\usepackage[utf8]{inputenc}
\usepackage{graphicx}     %% for graphical things such as including pictures
\usepackage{url}          %% for proper formatting of URLs

@@

\title{Guidelines for Designing Touch Interfaces for Controlling Robotic Nozzles in Critical Emergency Situations.}

% The abbreviated title will be shown in the headers of even pages.
% You should use the full title unless it is too long.
\titlerunning{Touch Interfaces for Robotic Nozzles in Emergency Situations}

@@

\subsection{Design of an A/B test}
In order to test if increased color contrast in a touch interface can  completely remove all faulty interactions an A/B test will be performed. Two identical applications, despite differences in color contrast, with just a few buttons will be measured against each other. We will measure time and errors. The test will have a time pressure to simulate an emergency situation. Instructions will be given on a secondary screen.
\emph{This section will contain a short but descriptive text about how the A/B test was prepared, built and performed. It will describe who participated}.

@@

\bibliography{Bibliography}
